Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2017-01-11 MovePattern_IJGI/ijgi-148112-for proofreading/oo.tex
Clean up

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly post messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

@@

In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section. Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.

@@

The above analysis of Twitter user mobility patterns mainly focuses on the spatiotemporal aspects.
Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis.
In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
The movement flows are obtained by aggregating the movements that started from and ended in the corresponding spatial units within the giving time frame.
In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states (Figure~\ref{fig:state_flow}).
It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\bibname{References}
\begin{thebibliography}{-------}
\providecommand{\natexlab}[1]{#1}
\providecommand{\natexlab}[1]{#1}

\bibitem[Zheng \em{et~al.}(2008)Zheng, Li, Chen, Xie, and
  Ma]{zheng2008understanding}
Zheng, Y.; Li, Q.; Chen, Y.; Xie, X.; Ma, W.Y.
\newblock Understanding mobility based on GPS data.
\newblock  Proceedings of the 10th international conference on Ubiquitous
  computing. ACM,  2008, pp. 312--321.

\bibitem[Jiang \em{et~al.}(2009)Jiang, Yin, and Zhao]{jiang2009characterizing}
Jiang, B.; Yin, J.; Zhao, S.
\newblock Characterizing the human mobility pattern in a large street network.
\newblock {\em Physical Review E} {\bf 2009}, {\em 80},~021136.

\bibitem[Belik \em{et~al.}(2011)Belik, Geisel, and Brockmann]{belik2011natural}
Belik, V.; Geisel, T.; Brockmann, D.
\newblock Natural human mobility patterns and spatial spread of infectious
  diseases.
\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.

\bibitem[Greenwood(1985)]{greenwood1985human}
Greenwood, M.J.
\newblock Human migration: Theory, models, and empirical studies.
\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.

@@

\bibitem[Jurdak \em{et~al.}(2015)Jurdak, Zhao, Liu, AbouJaoude, Cameron, and
  Newth]{Jurdak2015}
Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
\newblock Understanding Human Mobility from Twitter.
\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.

\bibitem[Rhee \em{et~al.}(2011)Rhee, Shin, Hong, Lee, Kim, and
  Chong]{rhee2011levy}
Rhee, I.; Shin, M.; Hong, S.; Lee, K.; Kim, S.J.; Chong, S.
\newblock On the levy-walk nature of human mobility.
\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
  19},~630--643.

\bibitem[Sevtsuk and Ratti(2010)]{sevtsuk2010does}
Sevtsuk, A.; Ratti, C.
\newblock Does urban mobility have a daily routine? Learning from the aggregate
  data of mobile networks.
\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.

\bibitem[Kung \em{et~al.}(2014)Kung, Greco, Sobolevsky, and
  Ratti]{kung2014exploring}
Kung, K.S.; Greco, K.; Sobolevsky, S.; Ratti, C.
\newblock Exploring universal patterns in human home-work commuting from mobile
  phone data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.

\bibitem[Thatcher(2014)]{thatcher2014living}
Thatcher, J.
\newblock Living on fumes: Digital footprints, data fumes, and the limitations
  of spatial big data.
\newblock {\em International Journal of Communication} {\bf 2014}, {\em
  8},~1765--1783.

\bibitem[Hawelka \em{et~al.}(2014)Hawelka, Sitko, Beinat, Sobolevsky,
  Kazakopoulos, and Ratti]{hawelka2014geo}
Hawelka, B.; Sitko, I.; Beinat, E.; Sobolevsky, S.; Kazakopoulos, P.; Ratti, C.
\newblock Geo-located Twitter as proxy for global mobility patterns.
\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
  41},~260--271.

\bibitem[Giannotti and Pedreschi(2008)]{giannotti2008mobility}
Giannotti, F.; Pedreschi, D.
\newblock {\em Mobility, data mining and privacy: Geographic knowledge
  discovery}; Springer Science \& Business Media,  2008.

\bibitem[Crampton(2014)]{crampton2014collect}
Crampton, J.W.
\newblock Collect it all: national security, Big Data and governance.
\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.

\bibitem[Wu \em{et~al.}(2014)Wu, Zhi, Sui, and Liu]{wu2014intra}
Wu, L.; Zhi, Y.; Sui, Z.; Liu, Y.
\newblock Intra-urban human mobility and activity transition: Evidence from
  social media check-in data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.

\bibitem[Hasan \em{et~al.}(2013)Hasan, Zhan, and
  Ukkusuri]{hasan2013understanding}
Hasan, S.; Zhan, X.; Ukkusuri, S.V.
\newblock Understanding urban human activity and mobility patterns using
  large-scale location-based data from online social media.
\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
  computing. ACM,  2013, p.~6.

\bibitem[Cho \em{et~al.}(2011)Cho, Myers, and Leskovec]{cho2011friendship}
Cho, E.; Myers, S.A.; Leskovec, J.
\newblock Friendship and mobility: user movement in location-based social
  networks.
\newblock  Proceedings of the 17th ACM SIGKDD international conference on
  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.

\bibitem[Noulas \em{et~al.}(2012)Noulas, Scellato, Lambiotte, Pontil, and
  Mascolo]{noulas2012tale}
Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
\newblock A tale of many cities: universal patterns in human urban mobility.
\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.

\bibitem[Balcan \em{et~al.}(2009)Balcan, Colizza, Gon{\c{c}}alves, Hu, Ramasco,
  and Vespignani]{balcan2009multiscale}
Balcan, D.; Colizza, V.; Gon{\c{c}}alves, B.; Hu, H.; Ramasco, J.J.;
  Vespignani, A.
\newblock Multiscale mobility networks and the spatial spreading of infectious
  diseases.
\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
  {\em 106},~21484--21489.

\bibitem[Tamerius \em{et~al.}(2011)Tamerius, Nelson, Zhou, Viboud, Miller, and
  Alonso]{tamerius2011global}
Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
\newblock Global influenza seasonality: reconciling patterns across temperate
  and tropical regions.
\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.

\bibitem[Tsou(2015)]{tsou2015}
Tsou, M.H.
\newblock Research challenges and opportunities in mapping social media and Big
  Data.
\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
  42},~70--74.

\bibitem[Zheng \em{et~al.}(2010)Zheng, Xie, and Ma]{zheng2010geolife}
Zheng, Y.; Xie, X.; Ma, W.Y.
\newblock GeoLife: A Collaborative Social Networking Service among User,
  Location and Trajectory. {\bf 2010}.

\bibitem[Becker \em{et~al.}(2013)Becker, C{\'a}ceres, Hanson, Isaacman, Loh,
  Martonosi, Rowland, Urbanek, Varshavsky, and Volinsky]{becker2013human}
Becker, R.; C{\'a}ceres, R.; Hanson, K.; Isaacman, S.; Loh, J.M.; Martonosi,
  M.; Rowland, J.; Urbanek, S.; Varshavsky, A.; Volinsky, C.
\newblock Human mobility characterization from cellular network data.
\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.

\bibitem[Sobolevsky \em{et~al.}(2013)Sobolevsky, Szell, Campari, Couronn{\'e},
  Smoreda, and Ratti]{sobolevsky2013delineating}
Sobolevsky, S.; Szell, M.; Campari, R.; Couronn{\'e}, T.; Smoreda, Z.; Ratti,
  C.
\newblock Delineating geographical regions with networks of human interactions
  in an extensive set of countries.
\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.

\bibitem[Twitter(2016)]{twitterAPI}
Twitter.
\newblock Twitter streaming API.
\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
  2016}.

\bibitem[Cranshaw \em{et~al.}(2012)Cranshaw, Schwartz, Hong, and
  Sadeh]{cranshaw2012livehoods}
Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
\newblock The Livehoods Project: Utilizing Social Media to Understand the
  Dynamics of a City.
\newblock  ICWSM,  2012.

\bibitem[Mitchell \em{et~al.}(2013)Mitchell, Frank, Harris, Dodds, and
  Danforth]{mitchell2013geography}
Mitchell, L.; Frank, M.R.; Harris, K.D.; Dodds, P.S.; Danforth, C.M.
\newblock The geography of happiness: Connecting twitter sentiment and
  expression, demographics, and objective characteristics of place {\bf 2013}.

\bibitem[Longley \em{et~al.}(2015)Longley, Adnan, Lansley,
  et~al.]{longley2015geotemporal}
Longley, P.A.; Adnan, M.; Lansley, G.; others.
\newblock The geotemporal demographics of Twitter usage.
\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.

\bibitem[H{\"a}gerstrand \em{et~al.}(1985)H{\"a}gerstrand
  et~al.]{hagerstrand1985time}
H{\"a}gerstrand, T.; others.
\newblock Time-geography: focus on the corporeality of man, society, and
  environment.
\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.

\bibitem[Kwan and Lee(2004)]{kwan2004geovisualization}
Kwan, M.P.; Lee, J.
\newblock Geovisualization of human activity patterns using 3D GIS: a
  time-geographic approach.
\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.

\bibitem[Andrienko and Andrienko(2007)]{andrienko2007designing}
Andrienko, N.; Andrienko, G.
\newblock Designing visual analytics methods for massive collections of
  movement data.
\newblock {\em Cartographica: The International Journal for Geographic
  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.

\bibitem[MacEachren and Kraak(2001)]{maceachren2001research}
MacEachren, A.M.; Kraak, M.J.
\newblock Research challenges in geovisualization.
\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
  28},~3--12.

\bibitem[MacEachren(2004)]{maceachren2004maps}
MacEachren, A.M.
\newblock {\em How maps work: representation, visualization, and design};
  Guilford Press,  2004.

\bibitem[Andrienko \em{et~al.}(2007)Andrienko, Andrienko, and
  Wrobel]{andrienko2007visual}
Andrienko, G.; Andrienko, N.; Wrobel, S.
\newblock Visual analytics tools for analysis of movement data.
\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.

\bibitem[Cao \em{et~al.}(2015)Cao, Wang, Hwang, Padmanabhan, Zhang, and
  Soltani]{cao2014scalable}
Cao, G.; Wang, S.; Hwang, M.; Padmanabhan, A.; Zhang, Z.; Soltani, K.
\newblock A scalable framework for spatiotemporal analysis of location-based
  social media data.
\newblock {\em Computers, Environment and Urban Systems} {\bf 2015}, {\em
  51},~70--82.

\bibitem[Padmanabhan \em{et~al.}(2014)Padmanabhan, Wang, Cao, Hwang, Zhang,
  Gao, Soltani, and Liu]{padmanabhan2014flumapper}
Padmanabhan, A.; Wang, S.; Cao, G.; Hwang, M.; Zhang, Z.; Gao, Y.; Soltani, K.;
  Liu, Y.
\newblock FluMapper: A cyberGIS application for interactive analysis of massive
  location-based social media.
\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
  2014}.

\bibitem[Black \em{et~al.}(2012)Black, Mascaro, Gallagher, and
  Goggins]{black2012twitter}
Black, A.; Mascaro, C.; Gallagher, M.; Goggins, S.P.
\newblock Twitter zombie: Architecture for capturing, socially transforming and
  analyzing the Twittersphere.
\newblock  Proceedings of the 17th ACM international conference on Supporting
  group work. ACM,  2012, pp. 229--238.

\bibitem[Shvachko \em{et~al.}(2010)Shvachko, Kuang, Radia, and
  Chansler]{shvachko2010hadoop}
Shvachko, K.; Kuang, H.; Radia, S.; Chansler, R.
\newblock The hadoop distributed file system.
\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
  Symposium on. IEEE,  2010, pp. 1--10.

\bibitem[Dean and Ghemawat(2008)]{dean2008mapreduce}
Dean, J.; Ghemawat, S.
\newblock MapReduce: simplified data processing on large clusters.
\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.

\bibitem[Gao \em{et~al.}(2012)Gao, Tang, and Liu]{gao2012exploring}
Gao, H.; Tang, J.; Liu, H.
\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
\newblock  ICWSM,  2012.

\bibitem[Buttenfield and McMaster(1991)]{buttenfield1991map}
Buttenfield, B.P.; McMaster, R.B.
\newblock {\em Map Generalization: Making rules for knowledge representation};
  Longman Scientific \& Technical New York,  1991.

\bibitem[Samet(1984)]{samet1984quadtree}
Samet, H.
\newblock The quadtree and related hierarchical data structures.
\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.

\bibitem[Clauset \em{et~al.}(2009)Clauset, Shalizi, and
  Newman]{clauset2009power}
Clauset, A.; Shalizi, C.R.; Newman, M.E.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.

>>>>

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly post messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API (https://dev.twitter.com/streaming/overview) for easy data access.
Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

@@

In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.

As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages (https://support.twitter.com/articles/18311-the-twitter-rules) in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}. 
In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section. Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.

@@

The above analysis of Twitter user mobility patterns mainly focuses on the spatiotemporal aspects.
Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis.
In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
The movement flows are obtained by aggregating the movements that started from and ended in the corresponding spatial units within the giving time frame.
In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\bibname{References}
\begin{thebibliography}{-------}
\providecommand{\natexlab}[1]{#1}

\bibitem[Zheng \em{et~al.}(2008)Zheng, Li, Chen, Xie, and
  Ma]{zheng2008understanding}
Zheng, Y.; Li, Q.; Chen, Y.; Xie, X.; Ma, W.Y.
\newblock Understanding mobility based on GPS data.
\newblock  In Proceedings of the 10th International Conference on Ubiquitous
  Computing, Seoul, South Korea, 21--24 September 2008.

\bibitem[Jiang \em{et~al.}(2009)Jiang, Yin, and Zhao]{jiang2009characterizing}
Jiang, B.; Yin, J.; Zhao, S.
\newblock Characterizing the human mobility pattern in a large street network.
\newblock {\em Phys. Rev. E} {\bf 2009}, doi:10.1103/PhysRevE.80.021136.

\bibitem[Belik \em{et~al.}(2011)Belik, Geisel, and Brockmann]{belik2011natural}
Belik, V.; Geisel, T.; Brockmann, D.
\newblock Natural human mobility patterns and spatial spread of infectious
  diseases.
\newblock {\em Phys. Rev. X} {\bf 2011}, doi:10.1103/PhysRevX.1.011001.

\bibitem[Greenwood(1985)]{greenwood1985human}
Greenwood, M.J.
\newblock Human migration: Theory, models, and empirical studies.
\newblock {\em J. Reg. Sci.} {\bf 1985}, {\em 25},~521--544.

@@

\bibitem[Jurdak \em{et~al.}(2015)Jurdak, Zhao, Liu, AbouJaoude, Cameron, and
  Newth]{Jurdak2015}
Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
\newblock Understanding human mobility from twitter.
\newblock {\em PLoS One} {\bf 2015}, doi:10.1371/journal.pone.0131469.

\bibitem[Rhee \em{et~al.}(2011)Rhee, Shin, Hong, Lee, Kim, and
  Chong]{rhee2011levy}
Rhee, I.; Shin, M.; Hong, S.; Lee, K.; Kim, S.J.; Chong, S.
\newblock On the levy-walk nature of human mobility.
\newblock {\em IEEE/ACM Trans. Netw.} {\bf 2011}, {\em
  19},~630--643.

\bibitem[Sevtsuk and Ratti(2010)]{sevtsuk2010does}
Sevtsuk, A.; Ratti, C.
\newblock Does urban mobility have a daily routine? Learning from the aggregate
  data of mobile networks.
\newblock {\em J. Urban Technol.} {\bf 2010}, {\em 17},~41--60.

\bibitem[Kung \em{et~al.}(2014)Kung, Greco, Sobolevsky, and
  Ratti]{kung2014exploring}
Kung, K.S.; Greco, K.; Sobolevsky, S.; Ratti, C.
\newblock Exploring universal patterns in human home-work commuting from mobile
  phone data.
\newblock {\em PloS One} {\bf 2014}, doi:10.1371/journal.pone.0096180.

\bibitem[Thatcher(2014)]{thatcher2014living}
Thatcher, J.
\newblock Living on fumes: Digital footprints, data fumes, and the limitations
  of spatial big data.
\newblock {\em Int. J. Commun.} {\bf 2014}, {\em
  8},~1765--1783.

\bibitem[Hawelka \em{et~al.}(2014)Hawelka, Sitko, Beinat, Sobolevsky,
  Kazakopoulos, and Ratti]{hawelka2014geo}
Hawelka, B.; Sitko, I.; Beinat, E.; Sobolevsky, S.; Kazakopoulos, P.; Ratti, C.
\newblock Geo-located Twitter as proxy for global mobility patterns.
\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2014}, {\em
  41},~260--271.

\bibitem[Giannotti and Pedreschi(2008)]{giannotti2008mobility}
Giannotti, F.; Pedreschi, D.
\newblock {\em Mobility, Data Mining and Privacy: Geographic Knowledge
  Discovery}; Springer Science \& Business Media: Berlin, Germany,  2008.

\bibitem[Crampton(2014)]{crampton2014collect}
Crampton, J.W.
\newblock Collect it all: National security, Big Data and governance.
\newblock {\em GeoJournal} {\bf 2014}, {\em 9}, 1--13.

\bibitem[Wu \em{et~al.}(2014)Wu, Zhi, Sui, and Liu]{wu2014intra}
Wu, L.; Zhi, Y.; Sui, Z.; Liu, Y.
\newblock Intra-urban human mobility and activity transition: Evidence from
  social media check-in data.
\newblock {\em PLoS one} {\bf 2014}, doi:10.1371/journal.pone.0097010.

\bibitem[Hasan \em{et~al.}(2013)Hasan, Zhan, and
  Ukkusuri]{hasan2013understanding}
Hasan, S.; Zhan, X.; Ukkusuri, S.V.
\newblock Understanding urban human activity and mobility patterns using
  large-scale location-based data from online social media.
\newblock  In Proceedings of the 2nd ACM SIGKDD International Workshop on Urban
  Computing, Chicago, IL, USA, 11--14 August 2013.

\bibitem[Cho \em{et~al.}(2011)Cho, Myers, and Leskovec]{cho2011friendship}
Cho, E.; Myers, S.A.; Leskovec, J.
\newblock Friendship and mobility: User movement in location-based social
  networks.
\newblock  In Proceedings of the 17th ACM SIGKDD International Conference on
  Knowledge Discovery and Data Mining, San Diego, CA, USA, 21--24 August 2011.

\bibitem[Noulas \em{et~al.}(2012)Noulas, Scellato, Lambiotte, Pontil, and
  Mascolo]{noulas2012tale}
Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
\newblock A tale of many cities: Universal patterns in human urban mobility.
\newblock {\em PLoS One} {\bf 2012}, doi:10.1371/journal.pone.0037027.

\bibitem[Balcan \em{et~al.}(2009)Balcan, Colizza, Gon{\c{c}}alves, Hu, Ramasco,
  and Vespignani]{balcan2009multiscale}
Balcan, D.; Colizza, V.; Gon{\c{c}}alves, B.; Hu, H.; Ramasco, J.J.;
  Vespignani, A.
\newblock Multiscale mobility networks and the spatial spreading of infectious
  diseases.
\newblock {\em Proc. Nat. Acad. Sci.} {\bf 2009},
  {\em 106},~21484--21489.

\bibitem[Tamerius \em{et~al.}(2011)Tamerius, Nelson, Zhou, Viboud, Miller, and
  Alonso]{tamerius2011global}
Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
\newblock Global influenza seasonality: Reconciling patterns across temperate
  and tropical regions.
\newblock {\em Environ. Health Perspect.} {\bf 2011}, {\em 119},~439--445.

\bibitem[Tsou(2015)]{tsou2015}
Tsou, M.H.
\newblock Research challenges and opportunities in mapping social media and Big
  Data.
\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2015}, {\em
  42},~70--74.

\bibitem[Zheng \em{et~al.}(2010)Zheng, Xie, and Ma]{zheng2010geolife}
Zheng, Y.; Xie, X.; Ma, W.Y.
\newblock GeoLife: A collaborative social networking service among user,
  location and trajectory. {\em IEEE Data(base) Eng. Bulletin} {\bf 2010}, {\em 33}, 32--39.

\bibitem[Becker \em{et~al.}(2013)Becker, C{\'a}ceres, Hanson, Isaacman, Loh,
  Martonosi, Rowland, Urbanek, Varshavsky, and Volinsky]{becker2013human}
Becker, R.; C{\'a}ceres, R.; Hanson, K.; Isaacman, S.; Loh, J.M.; Martonosi,
  M.; Rowland, J.; Urbanek, S.; Varshavsky, A.; Volinsky, C.
\newblock Human mobility characterization from cellular network data.
\newblock {\em Commun. ACM} {\bf 2013}, {\em 56},~74--82.

\bibitem[Sobolevsky \em{et~al.}(2013)Sobolevsky, Szell, Campari, Couronn{\'e},
  Smoreda, and Ratti]{sobolevsky2013delineating}
Sobolevsky, S.; Szell, M.; Campari, R.; Couronn{\'e}, T.; Smoreda, Z.; Ratti,
  C.
\newblock Delineating geographical regions with networks of human interactions
  in an extensive set of countries.
\newblock {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0081707.

\bibitem[Cranshaw \em{et~al.}(2012)Cranshaw, Schwartz, Hong, and
  Sadeh]{cranshaw2012livehoods}
Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
\newblock The livehoods project: Utilizing social media to understand the
  dynamics of a city.
\newblock  In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.

\bibitem[Mitchell \em{et~al.}(2013)Mitchell, Frank, Harris, Dodds, and
  Danforth]{mitchell2013geography}
Mitchell, L.; Frank, M.R.; Harris, K.D.; Dodds, P.S.; Danforth, C.M.
\newblock The geography of happiness: Connecting twitter sentiment and
  expression, demographics, and objective characteristics of place. {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0064417.

\bibitem[Longley \em{et~al.}(2015)Longley, Adnan, Lansley,
  et~al.]{longley2015geotemporal}
Longley, P.A.; Adnan, M.; Lansley, G.
\newblock The geotemporal demographics of Twitter usage.
\newblock {\em Environ. Plan. A} {\bf 2015}, {\em 47},~465--484.

\bibitem[H{\"a}gerstrand \em{et~al.}(1985)H{\"a}gerstrand
  et~al.]{hagerstrand1985time}
H{\"a}gerstrand, T.
\newblock Time-geography: Focus on the corporeality of man, society, and
  environment.
\newblock In {\em The Science and Praxis of Complexity}; United Nations University: Montpellier, France, 1985; pp. 193--216.

\bibitem[Kwan and Lee(2004)]{kwan2004geovisualization}
Kwan, M.P.; Lee, J.
\newblock Geovisualization of human activity patterns using 3D GIS: A
  time-geographic approach. In 
\newblock {\em Spatially Integrated Social Science: Examples in Best Practice}; Michael, F.G., Donald, G.J. Eds.; Oxford University Press: Oxford, MI, USA, 2003; Volume 3, pp. 27--51.

\bibitem[Andrienko and Andrienko(2007)]{andrienko2007designing}
Andrienko, N.; Andrienko, G.
\newblock Designing visual analytics methods for massive collections of
  movement data.
\newblock {\em Cartogr. Int. J. Geogr.
  Inf. Geovis.} {\bf 2007}, {\em 42},~117--138.

\bibitem[MacEachren and Kraak(2001)]{maceachren2001research}
MacEachren, A.M.; Kraak, M.J.
\newblock Research challenges in geovisualization.
\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2001}, {\em
  28},~3--12.

\bibitem[MacEachren(2004)]{maceachren2004maps}
MacEachren, A.M.
\newblock {\em How Maps Work: Representation, Visualization, and Design};
  Guilford Press: New York, NY, USA, 2004.

\bibitem[Andrienko \em{et~al.}(2007)Andrienko, Andrienko, and
  Wrobel]{andrienko2007visual}
Andrienko, G.; Andrienko, N.; Wrobel, S.
\newblock Visual analytics tools for analysis of movement data.
\newblock {\em ACM SIGKDD Explor. Newsl.} {\bf 2007}, {\em 9},~38--46.

\bibitem[Cao \em{et~al.}(2015)Cao, Wang, Hwang, Padmanabhan, Zhang, and
  Soltani]{cao2014scalable}
Cao, G.; Wang, S.; Hwang, M.; Padmanabhan, A.; Zhang, Z.; Soltani, K.
\newblock A scalable framework for spatiotemporal analysis of location-based
  social media data.
\newblock {\em Comput. Environ. Urban Syst.} {\bf 2015}, {\em 51}, 70--82.

\bibitem[Padmanabhan \em{et~al.}(2014)Padmanabhan, Wang, Cao, Hwang, Zhang,
  Gao, Soltani, and Liu]{padmanabhan2014flumapper}
Padmanabhan, A.; Wang, S.; Cao, G.; Hwang, M.; Zhang, Z.; Gao, Y.; Soltani, K.;
  Liu, Y.
\newblock FluMapper: A cyberGIS application for interactive analysis of massive
  location-based social media.
\newblock {\em Concurr. Comput. Pract. Exp.} {\bf
  2014}, doi:10.1002/cpe.3287.

\bibitem[Shvachko \em{et~al.}(2010)Shvachko, Kuang, Radia, and
  Chansler]{shvachko2010hadoop}
Shvachko, K.; Kuang, H.; Radia, S.; Chansler, R.
\newblock The hadoop distributed file system.
\newblock  {\em Mass Storage Syst. Technol.}  {\bf 2010}, doi:10.1109/MSST.2010.5496972.

\bibitem[Dean and Ghemawat(2008)]{dean2008mapreduce}
Dean, J.; Ghemawat, S.
\newblock MapReduce: Simplified data processing on large clusters.
\newblock {\em Commun. ACM} {\bf 2008}, {\em 51},~107--113.

\bibitem[Gao \em{et~al.}(2012)Gao, Tang, and Liu]{gao2012exploring}
Gao, H.; Tang, J.; Liu, H.
\newblock Exploring social-historical ties on location-based social networks.
\newblock In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.

\bibitem[Buttenfield and McMaster(1991)]{buttenfield1991map}
Buttenfield, B.P.; McMaster, R.B.
\newblock {\em Map Generalization: Making Rules for Knowledge Representation};
  Longman Scientific \& Technical: New York, NY, USA, 1991.

\bibitem[Samet(1984)]{samet1984quadtree}
Samet, H.
\newblock The quadtree and related hierarchical data structures.
\newblock {\em ACM Comput. Surv. (CSUR)} {\bf 1984}, {\em 16},~187--260.

\bibitem[Clauset \em{et~al.}(2009)Clauset, Shalizi, and
  Newman]{clauset2009power}
Clauset, A.; Shalizi, C.R.; Newman, M.E.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM Rev.} {\bf 2009}, {\em 51},~661--703.

\bibitem[Reynolds(2012)]{reynolds2012truncated}
Reynolds, A.
\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
  collection when correlated random walks embody observed movement patterns.
\newblock {\em J. Royal Soc. Int.} {\bf 2012}, {\em
  9},~528--534.
